%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Conference proceedings}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\nocite{*}

% Paste output of .bbl publication list here

\textbf{Note:} Incomplete listing of conference proceedings.

\begin{thebibliography}{}

  \bibitem[Anderson et~al., 1999]{anderson1999upwelling}
  Anderson, R., Smit, A., and Levitt, G. (1999).
  \newblock Upwelling and fish-factory waste as nitrogen sources for suspended
    cultivation of \emph{Gracilaria gracilis} in saldanha bay, {S}outh {A}frica.
  \newblock In {\em Sixteenth International Seaweed Symposium}, pages 455--462.
    Springer, Dordrecht.
  
  \bibitem[Cisneros et~al., 2009]{cisneros2009impact}
  Cisneros, K.~O., Schoeman, D.~S., Laudien, J., and Smit, A. (2009).
  \newblock The impact of a temporarily open/closed estuary on the community
    structure of a sandy beach macrobenthos in {K}wa{Z}ulu-{N}atal, {S}outh
    {A}frica.
  \newblock In {\em Proceedings of the 5th International Symposium on Sandy
    Beaches}, pages 137--138. University of the Sunshine Coast, Queensland.
  
  \bibitem[de~Charmoy and de~Lecea, 2011]{deCharmoy2011chemical}
  de~Charmoy, L., S.~A. and de~Lecea, A. (2011).
  \newblock Chemical lipid-extraction and lipid correction techniques: Their use
    in stable isotopic trophodynamic studies in the {N}atal {B}ight, {S}outh
    {A}frica.
  \newblock In {\em 7th Western Indian Ocean Marine Science Association}.
  
  \bibitem[de~Lecea and A.J., 2011a]{deLecea2011effects}
  de~Lecea, A.M., O. A. C.~R. and A.J., S. (2011a).
  \newblock The effects of preservation methods, dyes and acidification on the
    isotopic values (δ15{N} and δ13{C}) of two zooplankton species from the
    {K}wa{Z}ulu-{N}atal {B}ight, {S}outh {A}frica.
  \newblock In {\em Australasian Environmental Isotope Conference \& 4th
    Australasian Hydrogeology Research Conference}.
  
  \bibitem[de~Lecea and A.J., 2011b]{deLecea2011preservation}
  de~Lecea, A.M., O. A. C.~R. and A.J., S. (2011b).
  \newblock The effects of preservation methods, dyes and acidification on the
    isotopic values (δ15{N} and δ13{C}) of two zooplankton species from the
    {K}wa{Z}ulu-{N}atal {B}ight, {S}outh {A}frica.
  \newblock In {\em 14th South African Marine Science Symposium \& 49th Estuarine
    and Coastal Sciences Association International Conference}.
  
  \bibitem[de~Lecea and Fennessy, 2011a]{deLecea2011freezethaw}
  de~Lecea, A.M., S.~A. and Fennessy, S. (2011a).
  \newblock The effects of freeze-thaw periods and drying methods on isotopic and
    elemental carbon and nitrogen in marine organisms.
  \newblock In {\em 11th Australasian Environmental Isotope Conference \& 4th
    Australasian Hydrogeology Research Conference}.
  
  \bibitem[de~Lecea and Fennessy, 2011b]{deLecea2011the}
  de~Lecea, A.M., S.~A. and Fennessy, S. (2011b).
  \newblock The effects of freeze-thaw periods and drying methods on isotopic and
    elemental carbon and nitrogen in marine organisms.
  \newblock In {\em 14th South African Marine Science Symposium \& 49th Estuarine
    and Coastal Sciences Association International Conference}.
  
  \bibitem[de~Lecea and S.T., 2014]{deLecea2014what}
  de~Lecea, A.M., S.~A. and S.T., F. (2014).
  \newblock What drives the ecosystem of the {K}wa{Z}ulu-{N}atal {B}ight?
    {P}rocesses controlling the marine ecosystem of a mesotrophic bight revealed
    by stable isotope and {C:N} ratio analyses.
  \newblock In {\em 15th South African Marine Science Symposium}.
  
  \bibitem[de~Lecea and Charmoy, 2014]{deLecea2014chemical}
  de~Lecea, A.M., S. A. F.~S. and Charmoy, L. (2014).
  \newblock Chemical lipid-extraction and lipid correction techniques: Their use
    in stable isotopic trophodynamic studies of deep-water species of the
    {K}wa{Z}ulu-{N}atal {B}ight.
  \newblock In {\em 15th South African Marine Science Symposium}.
  
  \bibitem[Fitchett et~al., 2020]{fitchett2020early}
  Fitchett, J., Smit, A.~J., and Sweijd, N. (2020).
  \newblock Early research on {COVID}-19 and climate: {A} bibliometrics analysis.
  \newblock {\em Climatological, Meteorological, and Environmental factors in the
    COVID-19 pandemic}.
  
  \bibitem[Omarjee and A.J., 2014]{omarjee2014nutrient}
  Omarjee, A., d. L.~A. and A.J., S. (2014).
  \newblock Nutrient uptake in the kwazulu-natal.
  \newblock In {\em 15th South African Marine Science Symposium}.
  
  \bibitem[Rautenbach et~al., 2018]{rautenbach2018spatial}
  Rautenbach, C., Reddy, M., Williams, L., and Smit, A.~J. (2018).
  \newblock Spatial relationship between nearshore physical drivers and seaweed
    community and genetic data around the cape peninsula, {S}outh {A}frica.
  \newblock In {\em 2018 Ocean Sciences Meeting}. AGU.
  
  \bibitem[Robertson-Andersson et~al., 2005]{robertson2005effect}
  Robertson-Andersson, D., Smit, A., Peall, S., and Bolton, J. (2005).
  \newblock The effect of diet on {DMSP} accumulation and taste in {S}outh
    {A}frican abalone (\emph{Haliotis midae}).
  \newblock In {\em Phycologia}, volume~44, pages 86--87. International
    Phycological Society.
  
  \bibitem[Rothman et~al., 2006]{rothman2006effects}
  Rothman, M., Anderson, R., and Smit, A. (2006).
  \newblock The effects of harvesting of the {S}outh {A}frican kelp
    (\emph{Ecklonia maxima}) on kelp population structure, growth rate and
    recruitment.
  \newblock In {\em Eighteenth International Seaweed Symposium}, pages 109--115.
    Springer, Dordrecht.
  
  \bibitem[Rothman et~al., 2002]{rothman2002using}
  Rothman, M., Anderson, R., Smit, A., Kemp, F., and Boothroyd, C. (2002).
  \newblock Using forest demographic methods to study the effects of kelp
    (\emph{Ecklonia maxima}) harvesting.
  \newblock In {\em Southern African Marine Science Symposium (SAMSS 2002):
    Currents Coasts Communities. vp. 2002.}
  
  \bibitem[Schoeman et~al., 2009]{schoeman2009illustration}
  Schoeman, D.~S., Scharler, U., and Smit, A. (2009).
  \newblock An illustration of the importance of sandy beaches to coastal
    ecosystem services at the regional scale.
  \newblock In {\em Sandy Beaches and Coastal Zone Management. Proceedings of the
    Fifth International Symposium on Sandy Beaches, 19th-23rd October}, page
    139e140.
  
  \bibitem[Schoeman et~al., 2008]{schoeman2008squeezed}
  Schoeman, D.~S., Smit, A., Scharler, U., Muir, D., Govender, N., Harris, L.,
    and Nel, R. (2008).
  \newblock Squeezed out: sandy beaches as threatened functional ecosystems.
  \newblock In {\em World Conference on Marine Biodiversity}. University of the
    Sunshine Coast, Queensland.
  
  \bibitem[Smit et~al., 2002]{smit2002comparisons}
  Smit, A., Brearley, A., Hyndes, G., Lavery, P., Walker, D., Vanderklift, M.,
    and Gartner, A. (2002).
  \newblock Comparisons of {C} and {N} transfer within and between four types of
    marine habitats off {W}estern {A}ustralia.
  \newblock In {\em Southern African Marine Science Symposium (SAMSS 2002):
    Currents Coasts Communities. vp. 2002.}
  
  \bibitem[Smit et~al., 2014]{smit2014coupling}
  Smit, A., de~Lecea, A., Omarjee, A., and Fennessy, S. (2014).
  \newblock Coupling physical processes of the {K}wa{Z}ulu-{N}atal {B}ight
    ({S}outh {A}frica) to the ecosystem function of its pelagic and benthic food
    webs.
  \newblock In {\em 9th International IsoEcol Conference}.
  
  \bibitem[Smit et~al., 2017]{smit2017variability}
  Smit, A., Dyer, D., Bolton, J., and Anderson, R. (2017).
  \newblock {V}ariability in stable isotope signatures of {S}outh {A}frican
    {L}aminariales.
  \newblock In {\em 11th International Phycological Congress}.
  
  \bibitem[Smit et~al., 2018]{smit2018amarine}
  Smit, A.~J., Schlegel, R.~W., and Williamson, R. (2018).
  \newblock {A} {M}arine {H}eat {W}ave {A}nalysis of the {W}estern {I}ndian
    {O}cean {R}eflects {L}ong-term {C}hanges in the {H}eat {C}onveying {D}ynamics
    of the {A}gulhas {C}urrent.
  \newblock In {\em 2018 Ocean Sciences Meeting}. AGU.
  
  \bibitem[Smit and de~Lecea, 2011]{deLecea2011fluvial}
  Smit, A.J., F.~S. and de~Lecea, A. (2011).
  \newblock Fluvial materials as drivers of inshore processes in the central
    {K}wa{Z}ulu-{N}atal {B}ight, {S}outh {A}frica.
  \newblock In {\em 7th Western Indian Ocean Marine Science Association}.
  
  \end{thebibliography}
  