%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Publications}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\nocite{*}

% Paste output of .bbl publication list here

\begin{thebibliography}{}

  \bibitem[Abrahams et~al., 2021a]{abrahams2021novel}
  Abrahams, A., Schlegel, R.~W., and Smit, A.~J. (2021a).
  \newblock A novel approach to quantify metrics of upwelling intensity,
    frequency, and duration.
  \newblock {\em Plos one}, 16(7):e0254026.
  
  \bibitem[Abrahams et~al., 2021b]{abrahams2021variation}
  Abrahams, A., Schlegel, R.~W., and Smit, A.~J. (2021b).
  \newblock Variation and change of upwelling dynamics detected in the world’s
    eastern boundary upwelling systems.
  \newblock {\em Frontiers in Marine Science}, page~29.
  
  \bibitem[Anderson et~al., 1998]{anderson1998differential}
  Anderson, B., Smit, A., and Bolton, J. (1998).
  \newblock Differential grazing effects by isopods on \emph{Gracilaria gracilis}
    and epiphytic \emph{Ceramium diaphanum} in suspended raft culture.
  \newblock {\em Aquaculture}, 169(1-2):99--109.
  
  \bibitem[Anderson et~al., 2012]{anderson2012seaweeds}
  Anderson, R., Bolton, J., Smit, A., and da~Neto-Silva, D. (2012).
  \newblock The seaweeds of {A}ngola: the transition between tropical and
    temperate marine floras on the west coast of southern {A}frica.
  \newblock {\em African Journal of Marine Science}, 34(1):1--13.
  
  \bibitem[Bolton et~al., 2012]{bolton2012south}
  Bolton, J., Anderson, R., Smit, A., and Rothman, M. (2012).
  \newblock {S}outh {A}frican kelp moving eastwards: the discovery of
    \emph{Ecklonia maxima} ({O}sbeck) {P}apenfuss at {D}e {H}oop {N}ature
    {R}eserve on the south coast of {S}outh {A}frica.
  \newblock {\em African Journal of Marine Science}, 34(1):147--151.
  
  \bibitem[Bornman et~al., 2016]{bornman2016relative}
  Bornman, T., Schmidt, J., Adams, J., Mfikili, A., Farre, R., and Smit, A.
    (2016).
  \newblock Relative sea-level rise and the potential for subsidence of the
    {S}wartkops {E}stuary intertidal salt marshes, {S}outh {A}frica.
  \newblock {\em {S}outh {A}frican Journal of Botany}, 107:91--100.
  
  \bibitem[Botes et~al., 2003]{botes2003potential}
  Botes, L., Smit, A., and Cook, P. (2003).
  \newblock The potential threat of algal blooms to the abalone (\emph{Haliotis
    midae}) mariculture industry situated around the {S}outh {A}frican coast.
  \newblock {\em Harmful Algae}, 2(4):247--259.
  
  \bibitem[Cockburn et~al., 2016]{cockburn2016build}
  Cockburn, J., Rouget, M., Slotow, R., Roberts, D., Boon, R., Douwes, E.,
    O'Donoghue, S., Downs, C.~T., Mukherjee, S., Musakwa, W., et~al. (2016).
  \newblock How to build science-action partnerships for local land-use planning
    and management: lessons from durban, {S}outh {A}frica.
  \newblock {\em Ecology and Society}, 21(1).
  
  \bibitem[Cockburn et~al., ]{cockburnimplementation}
  Cockburn, J., Rouget, M., Slotow, R., Roberts, D., Boon, R., Douwes, E.,
    O’Donoghue, S., Downs, C., Mukherjee, S., Musakwa, W., et~al.
  \newblock Implementation of a science-action partnership to manage a threatened
    ecosystem in an urban context.
  \newblock {\em Ecology and Society}.
  
  \bibitem[Coppin et~al., 2020]{coppin2020investigating}
  Coppin, R., Rautenbach, C., Ponton, T.~J., and Smit, A. (2020).
  \newblock Investigating waves and temperature as drivers of kelp morphology.
  \newblock {\em Frontiers in Marine Science}, 7:567.
  
  \bibitem[Cotiyane et~al., 2017]{cotiyane2017towards}
  Cotiyane, P., Bornman, T., and Smit, A. (2017).
  \newblock Towards the biogeography of marine benthic diatoms along the coast of
    {S}outh {A}frica.
  \newblock {\em Phycologia}, 56(4):35.
  
  \bibitem[Cotiyane-Pondo et~al., 2020]{cotiyane2020austral}
  Cotiyane-Pondo, P., Bornman, T.~G., D{\k{a}}bek, P., Witkowski, A., and Smit,
    A.~J. (2020).
  \newblock Austral winter marine epilithic diatoms: Community composition and
    distribution on intertidal rocky substrate around the coast of {S}outh
    {A}frica.
  \newblock {\em Estuarine, Coastal and Shelf Science}, 242:106837.
  
  \bibitem[de~Lecea et~al., 2013]{de2013processes}
  de~Lecea, A., Fennessy, S., and Smit, A. (2013).
  \newblock Processes controlling the benthic food web of a mesotrophic bight
    ({K}wa{Z}ulu-{N}atal, {S}outh {A}frica) revealed by stable isotope analysis.
  \newblock {\em Marine Ecology Progress Series}, 484:97--114.
  
  \bibitem[de~Lecea et~al., 2011]{de2011effects}
  de~Lecea, A., Smit, A., and Fennessy, S. (2011).
  \newblock The effects of freeze/thaw periods and drying methods on isotopic and
    elemental carbon and nitrogen in marine organisms, raising questions on
    sample preparation.
  \newblock {\em Rapid Communications in Mass Spectrometry}, 25(23):3640--3649.
  
  \bibitem[de~Lecea et~al., 2016]{de2016riverine}
  de~Lecea, A., Smit, A.~J., and Fennessy, S. (2016).
  \newblock Riverine dominance of a nearshore marine demersal food web: evidence
    from stable isotope and {C}/{N} ratio analysis.
  \newblock {\em African Journal of Marine Science}, 38(sup1):S181--S192.
  
  \bibitem[de~Lecea et~al., 2015]{de2015identifying}
  de~Lecea, A.~M., Cooper, R., and Smit, A.~J. (2015).
  \newblock Identifying the drivers of the pelagic ecosystem of an oligotrophic
    bight ({K}wa{Z}ulu-{N}atal, {S}outh {A}frica) using stable isotopes
    ($\delta$13c, $\delta$15n) and {C}:{N} ratio analysis.
  \newblock {\em Marine and Freshwater Research}, 67(11):1750--1761.
  
  \bibitem[du~Plooy et~al., 2015]{du2015role}
  du~Plooy, S., Perissinotto, R., Smit, A., and Muir, D. (2015).
  \newblock Role of salinity, nitrogen fixation and nutrient assimilation in
    prolonged bloom persistence of \emph{Cyanothece} sp.~in lake st lucia,
    {S}outh {A}frica.
  \newblock {\em Aquatic Microbial Ecology}, 74(1):73--83.
  
  \bibitem[du~Plooy et~al., 2014]{du2014nitrogen}
  du~Plooy, S., Smit, A., Perissinotto, R., and Muir, D. (2014).
  \newblock Nitrogen uptake dynamics of a persistent cyanobacterium
    \emph{Cyanothece} sp.~bloom in {L}ake {S}t {L}ucia, {S}outh {A}frica.
  \newblock {\em African Journal of Marine Science}, 36(2):155--161.
  
  \bibitem[Dyer et~al., 2017]{dyer2017variability}
  Dyer, D., Bolton, J., Smit, A., and Anderson, R. (2017).
  \newblock Variability in stable isotope signatures of {S}outh {A}frican
    laminariales: implications for kelp forest food web studies.
  \newblock {\em Phycologia}, 56(4):47.
  
  \bibitem[Dyer et~al., 2019a]{dyer2019characterizing}
  Dyer, D., Butler, M., Smit, A., Anderson, R., and Bolton, J. (2019a).
  \newblock Characterizing kelp forest pom during upwelling and downwelling
    conditions: using stable isotope analysis to differentiate between detritus
    and phytoplankton.
  \newblock {\em Marine Ecology Progress Series}, 619:17--34.
  
  \bibitem[Dyer et~al., 2019b]{dyer2019kelp}
  Dyer, D.~C., Butler, M.~J., Smit, A.~J., Anderson, R.~J., and Bolton, J.~J.
    (2019b).
  \newblock Kelp forest {POM} during upwelling and downwelling conditions: using
    stable isotopes to differentiate between detritus and phytoplankton.
  \newblock {\em Marine Ecology Progress Series}, 619:17--34.
  
  \bibitem[Dyer et~al., 2019c]{dyer2019variability}
  Dyer, D.~C., Butler, M.~J., Smit, A.~J., Anderson, R.~J., and Bolton, J.~J.
    (2019c).
  \newblock Variability in stable isotope values of {S}outh {A}frican
    {L}aminariales, \emph{Ecklonia maxima} and \emph{Laminaria pallida}, over
    different spatial and temporal scales.
  \newblock {\em Marine Ecology Progress Series}, 628:55--71.
  
  \bibitem[Garc{\'\i}a-Reyes et~al., 2015]{garcia2015under}
  Garc{\'\i}a-Reyes, M., Sydeman, W.~J., Schoeman, D.~S., Rykaczewski, R.~R.,
    Black, B.~A., Smit, A.~J., and Bograd, S.~J. (2015).
  \newblock {U}nder pressure: {C}limate change, upwelling, and eastern boundary
    upwelling ecosystems.
  \newblock {\em Frontiers in Marine Science}, 2:109.
  
  \bibitem[Gartner et~al., 2002]{gartner2002use}
  Gartner, A., Lavery, P., and Smit, A. (2002).
  \newblock Use of $\delta$15{N} signatures of different functional forms of
    macroalgae and filter-feeders to reveal temporal and spatial patterns in
    sewage dispersal.
  \newblock {\em Marine Ecology Progress Series}, 235:63--73.
  
  \bibitem[Govender et~al., 2011]{govender2011trophic}
  Govender, N., Smit, A.~J., and Perissinotto, R. (2011).
  \newblock Trophic functioning of the st.~{L}ucia estuarine lake during a
    drought phase assessed using stable isotopes.
  \newblock {\em Estuarine, Coastal and Shelf Science}, 93(2):87--97.
  
  \bibitem[Kirsten et~al., 2018]{kirsten2018multiproxy}
  Kirsten, K.~L., Haberzettl, T., W{\"u}ndsch, M., Frenzel, P., Meschner, S.,
    Smit, A., Quick, L.~J., M{\"a}usbacher, R., and Meadows, M.~E. (2018).
  \newblock A multiproxy study of the ocean-atmospheric forcing and the impact of
    sea-level changes on the southern {C}ape coast, {S}outh {A}frica during the
    {H}olocene.
  \newblock {\em Palaeogeography, Palaeoclimatology, Palaeoecology},
    496:282--291.
  
  \bibitem[Livingstone et~al., 2018]{livingstone2018classification}
  Livingstone, T., Harris, J., Lombard, A., Smit, A., and Schoeman, D.~S. (2018).
  \newblock Classification of marine bioregions on the east coast of {S}outh
    {A}frica.
  \newblock {\em African Journal of Marine Science}, 40(1):51--65.
  
  \bibitem[Majewska et~al., 2022]{majewska2022new}
  Majewska, R., Mayombo, N.~A., Smit, A.~J., and Goosen, W.~E. (2022).
  \newblock New observations on the diatom genus \emph{Druehlago}
    (bacillariophyta) and description of two new species from {S}outh {A}frica.
  \newblock {\em Phycologia}, 61(1):75--88.
  
  \bibitem[Mass{\'e} et~al., ]{massesexual}
  Mass{\'e}, L., Schleyer, M., S{\'e}r{\'e}, M., and Smit, A.
  \newblock Sexual reproduction of the coral \emph{Pocillopora damicornis} at
    high latitude off the {D}urban coast.
  
  \bibitem[Masse et~al., 2012]{masse2012sexual}
  Masse, L.~M., S{\'e}r{\'e}, M.~G., Smit, A.~J., and Schleyer, M.~H. (2012).
  \newblock Sexual reproduction in \emph{Pocillopora damicornis} at high latitude
    off {S}outh {A}frica.
  \newblock {\em Western Indian Ocean Journal of Marine Science}, 11(1):55--65.
  
  \bibitem[Mayombo et~al., 2019]{mayombo2019diatoms}
  Mayombo, N., Majewska, R., and Smit, A. (2019).
  \newblock Diatoms associated with two {S}outh {A}frican kelp species:
    \emph{Ecklonia maxima} and \emph{Laminaria pallida}.
  \newblock {\em African Journal of Marine Science}, 41(2):221--229.
  
  \bibitem[Mayombo et~al., 2020]{mayombo2020assessment}
  Mayombo, N. A.~S., Majewska, R., and Smit, A.~J. (2020).
  \newblock An assessment of the influence of host species, age, and thallus part
    on kelp-associated diatoms.
  \newblock {\em Diversity}, 12(10):385.
  
  \bibitem[Naidoo et~al., 2015]{naidoo2015plastic}
  Naidoo, T., Glassom, D., and Smit, A.~J. (2015).
  \newblock Plastic pollution in five urban estuaries of {K}wa{Z}ulu-{N}atal,
    {S}outh {A}frica.
  \newblock {\em Marine pollution bulletin}, 101(1):473--480.
  
  \bibitem[Naidoo et~al., 2016]{naidoo2016plastic}
  Naidoo, T., Smit, A., and Glassom, D. (2016).
  \newblock Plastic ingestion by estuarine mullet \emph{Mugil cephalus}
    (mugilidae) in an urban harbour, {K}wa{Z}ulu-{N}atal, {S}outh {A}frica.
  \newblock {\em African Journal of Marine Science}, 38(1):145--149.
  
  \bibitem[Ortega et~al., ]{ortegaimpact}
  Ortega, K., Schoeman, D., Laudien, J., and Smit, A.
  \newblock The impact of a temporarily open/closed estuary on the community
    structure of a sandy beach macrobenthos in {K}wa{Z}ulu-{N}atal, {S}outh
    {A}frica.
  
  \bibitem[Ortega-Cisneros et~al., 2017]{ortega2017resource}
  Ortega-Cisneros, K., de~Lecea, A.~M., Smit, A.~J., and Schoeman, D.~S. (2017).
  \newblock Resource utilization and trophic niche width in sandy beach
    macrobenthos from an oligotrophic coast.
  \newblock {\em Estuarine, Coastal and Shelf Science}, 184:115--125.
  
  \bibitem[Ortega~Cisneros et~al., 2011]{ortega2011complex}
  Ortega~Cisneros, K., Smit, A.~J., Laudien, J., and Schoeman, D.~S. (2011).
  \newblock Complex, dynamic combination of physical, chemical and nutritional
    variables controls spatio-temporal variation of sandy beach community
    structure.
  \newblock {\em PLoS One}, 6(8):e23724.
  
  \bibitem[Pillay et~al., 2019]{pillay2019financing}
  Pillay, K., Kisten, Y., Smit, A., and Glassom, D. (2019).
  \newblock {F}inancing {E}mission {R}eductions.
  \newblock {\em Climate Change and Ocean Governance: Politics and Policy for
    Threatened Seas}, page 362.
  
  \bibitem[Ramdhani et~al., 2016]{ramdhani2016build}
  Ramdhani, S., Cockburn, J., Wale, E., Ray-Mukherjee, J., Proche{\c{s}}, S.,
    Mwabvu, T., Smit, A., Odindi, J., Musakwa, W., Willows-Munro, S., et~al.
    (2016).
  \newblock How to build science-action partnerships for local land use planning
    and management: Lessons from {D}urban, {S}outh {A}frica.
  
  \bibitem[Schlegel and Smit, 2016a]{schlegel2016effects}
  Schlegel, R. and Smit, A. (2016a).
  \newblock Effects of natural variability of seawater temperature, time series
    length, decadal trend and instrument precision on the ability to detect
    temperature trends.
  \newblock {\em Journal of Climate}, 29(24):9113--9124.
  
  \bibitem[Schlegel et~al., 2019]{schlegel2019detecting}
  Schlegel, R.~W., Oliver, E.~C., Hobday, A.~J., and Smit, A.~J. (2019).
  \newblock Detecting marine heatwaves with sub-optimal data.
  \newblock {\em Frontiers in Marine Science}, 6:737.
  
  \bibitem[Schlegel et~al., 2017a]{schlegel2017predominant}
  Schlegel, R.~W., Oliver, E.~C., Perkins-Kirkpatrick, S., Kruger, A., and Smit,
    A.~J. (2017a).
  \newblock Predominant atmospheric and oceanic patterns during coastal marine
    heatwaves.
  \newblock {\em Frontiers in Marine Science}, 4:323.
  
  \bibitem[Schlegel et~al., 2017b]{schlegel2017nearshore}
  Schlegel, R.~W., Oliver, E.~C., Wernberg, T., and Smit, A.~J. (2017b).
  \newblock Nearshore and offshore co-occurrence of marine heatwaves and
    cold-spells.
  \newblock {\em Progress in oceanography}, 151:189--205.
  
  \bibitem[Schlegel and Smit, 2016b]{schlegel2016climate}
  Schlegel, R.~W. and Smit, A.~J. (2016b).
  \newblock Climate change in coastal waters: time series properties affecting
    trend estimation.
  \newblock {\em Journal of Climate}, 29(24):9113--9124.
  
  \bibitem[Schlegel and Smit, 2018]{schlegel2018heatwaver}
  Schlegel, R.~W. and Smit, A.~J. (2018).
  \newblock heatwave{R}: A central algorithm for the detection of heatwaves and
    cold-spells.
  \newblock {\em Journal of Open Source Software}, 3(27):821.
  
  \bibitem[Smit, 2002]{smit2002nitrogen}
  Smit, A. (2002).
  \newblock Nitrogen uptake by \emph{Gracilaria gracilis} (rhodophyta):
    adaptations to a temporally variable nitrogen environment.
  
  \bibitem[Smit et~al., 2005]{smit2005carbon}
  Smit, A., Brearley, A., Hyndes, G., Lavery, P., and Walker, D. (2005).
  \newblock Carbon and nitrogen stable isotope analysis of an \emph{Amphibolis
    griffithii} seagrass bed.
  \newblock {\em Estuarine, Coastal and Shelf Science}, 65(3):545--556.
  
  \bibitem[Smit et~al., 2003]{smit2003control}
  Smit, A., Fourie, A., Robertson, B., and Du~Preez, D. (2003).
  \newblock Control of the herbivorous isopod, \emmph{Paridotea reticulata}, in
    \emph{Gracilaria gracilis} tank cultures.
  \newblock {\em Aquaculture}, 217(1-4):385--393.
  
  \bibitem[Smit et~al., 2010]{smit2010effect}
  Smit, A., Robertson-Andersson, D., and Bolton, J. (2010).
  \newblock The effect of macroalgal and compound feeds on the sensory quality of
    cultivated {S}outh {A}frican abalone, \emph{Haliotis midae} {L}innaeus
    ({M}ollusca, {G}astropoda).
  \newblock {\em Aquaculture nutrition}, 16(6):590--603.
  
  \bibitem[Smit, 1995]{smit1995optimising}
  Smit, A.~J. (1995).
  \newblock {\em Optimising \emph{Gracilaria verrucosa} production in a
    laboratory based culture system}.
  \newblock PhD thesis, University of Port Elizabeth.
  
  \bibitem[Smit, 1998]{smit1998nitrogen}
  Smit, A.~J. (1998).
  \newblock Nitrogen environment, ecophysiology and growth of \emph{Gracilaria
    gracilus} in {S}aldanha {B}ay, {S}outh {A}frica.
  
  \bibitem[Smit, 2001a]{smit2001food}
  Smit, A.~J. (2001a).
  \newblock {F}ood {W}eb {S}tudies using 13{C} and 15{N}.
  \newblock {\em Stable Isotope Techniques in the Study of Biological Processes
    and Functioning of Ecosystems}, 40:219.
  
  \bibitem[Smit, 2001b]{smit2001source}
  Smit, A.~J. (2001b).
  \newblock Source identification in marine ecosystems.
  \newblock In {\em Stable isotope techniques in the study of biological
    processes and functioning of ecosystems}, pages 219--245. Springer,
    Dordrecht.
  
  \bibitem[Smit, 2004]{smit2004medicinal}
  Smit, A.~J. (2004).
  \newblock Medicinal and pharmaceutical uses of seaweed natural products: {A}
    review.
  \newblock {\em Journal of Applied Phycology}, 16(4):245--262.
  
  \bibitem[Smit, 2013]{smit2013source}
  Smit, A.~J. (2013).
  \newblock {S}ource identification in {M}arine {E}cosystems.
  \newblock {\em Stable Isotope Techniques in the Study of Biological Processes
    and Functioning of Ecosystems}, 40:219.
  
  \bibitem[Smit and Bolton, 1999]{smit1999organismic}
  Smit, A.~J. and Bolton, J.~J. (1999).
  \newblock Organismic determinants and their effect on growth and regeneration
    in \emph{Gracilaria gracilis}.
  \newblock {\em Journal of applied phycology}, 11(3):293--299.
  
  \bibitem[Smit et~al., 2017]{smit2017seaweeds}
  Smit, A.~J., Bolton, J.~J., and Anderson, R.~J. (2017).
  \newblock Seaweeds in two oceans: beta-diversity.
  \newblock {\em Frontiers in Marine Science}, 4:404.
  
  \bibitem[Smit et~al., 2006]{smit2006delta15n}
  Smit, A.~J., Brearley, A., Hyndes, G.~A., Lavery, P.~S., and Walker, D.~I.
    (2006).
  \newblock $\delta$15{N} and $\delta$13{C} analysis of a \emph{Posidonia
    sinuosa} seagrass bed.
  \newblock {\em Aquatic Botany}, 84(3):277--282.
  
  \bibitem[Smit et~al., 2020]{smit2020winter}
  Smit, A.~J., Fitchett, J.~M., Engelbrecht, F.~A., Scholes, R.~J., Dzhivhuho,
    G., and Sweijd, N.~A. (2020).
  \newblock Winter is coming: a southern hemisphere perspective of the
    environmental drivers of {SARS-CoV-2} and the potential seasonality of
    {COVID-19}.
  \newblock {\em International journal of environmental research and public
    health}, 17(16):5634.
  
  \bibitem[Smit et~al., 2013]{smit2013coastal}
  Smit, A.~J., Roberts, M., Anderson, R.~J., Dufois, F., Dudley, S.~F., Bornman,
    T.~G., Olbers, J., and Bolton, J.~J. (2013).
  \newblock A coastal seawater temperature dataset for biogeographical studies:
    large biases between \emph{in situ} and remotely-sensed data sets around the
    coast of {S}outh {A}frica.
  \newblock {\em PLoS One}, 8(12):e81944.
  
  \bibitem[Smit et~al., 1996]{smit1996influence}
  Smit, A.~J., Robertson, B.~L., and du~Preez, D.~R. (1996).
  \newblock Influence of ammonium-{N} pulse concentrations and frequency, tank
    condition and nitrogen starvation on growth rate and biochemical composition
    of \emph{Gracilaria gracilis}.
  \newblock {\em Journal of Applied Phycology}, 8(6):473--481.
  
  \bibitem[Smit et~al., 2007]{smit2007dimethylsulfoniopropionate}
  Smit, A.~J., Robertson-Andersson, D.~V., Peall, S., and Bolton, J.~J. (2007).
  \newblock Dimethylsulfoniopropionate ({DMSP}) accumulation in abalone
    \emph{Haliotis midae} ({M}ollusca: {P}rosobranchia) after consumption of
    various diets, and consequences for aquaculture.
  \newblock {\em Aquaculture}, 269(1-4):377--389.
  
  \bibitem[Sweijd and Smit, 2020]{sweijd2020trends}
  Sweijd, N. and Smit, A. (2020).
  \newblock Trends in sea surface temperature and chlorophyll-a in the seven
    {A}frican {L}arge {M}arine {E}cosystems.
  \newblock {\em Environmental Development}, 36:100585.
  
  \bibitem[van Os et~al., 2012]{van2012influence}
  van Os, N., Mass{\'e}, L.~M., S{\'e}r{\'e}, M.~G., Sara, J.~R., Schoeman,
    D.~S., and Smit, A.~J. (2012).
  \newblock Influence of heterotrophic feeding on the survival and tissue growth
    rates of \emph{Galaxea fascicularis} ({O}ctocorralia: {O}cculinidae) in
    aquaria.
  \newblock {\em Aquaculture}, 330:156--161.
  
  \bibitem[Vanderklift et~al., 2006]{vanderklift2006differences}
  Vanderklift, M.~A., Kendrick, G.~A., and Smit, A.~J. (2006).
  \newblock Differences in trophic position among sympatric sea urchin species.
  \newblock {\em Estuarine, Coastal and Shelf Science}, 66(1-2):291--297.
  
\end{thebibliography}
  